Some examples in extended logic counting classes

### 2017-01-06 LICS/extentions.tex
Avance en sección extended.

>>>>

An interesting class of functions in complexity theory comes from considering the optimization version of a decision problem. For example, one can define MAX-SAT as the problem of determining the maximum number of clauses, of a given CNF formula, that can be made true by an assignment. Here, the problem is defined in terms of a maximization function and it is not known how to define this kind of function in $\shp$. 
To formalize this set of optimization problems, in~\cite{krentel1988complexity} the class $\optp$ was introduces as the class of functions computable by taking the maximum or minimum of the output values over all runs of a non-deterministic polynomial time machine with output (i.e. each run produces a binary string which is interpreted as a number). 
For instance, MAX-SAT is in $\optp$ with several other optimization version of $\np$-problems.
Given that in~\cite{krentel1988complexity} the author do not make the distinction between $\max$ or $\min$, in 
Given that

\begin{multline}
\alpha := \beta \ \mid \ s \ \mid \ (\, \max\{\alpha,\alpha\} \,) \ \mid\ (\, \min\{\alpha,\alpha\} \,) \ \mid \\ \maxa{x} \alpha \ \mid \ \mina{x} \alpha \ \mid \ \maxa{X} \alpha \ \mid \ \mina{X} \alpha 
\end{multline}
